The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach to measuring this factor.

3. Positive reinforcement: This can possibly be computed as an index and characterized on a scale even if this is not easy to quantify.

>>>>

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.

3. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute as an index and characterize it on a scale.
